### 2023-07-19 Rmd/Paper 03 short term forecast analysis.Rmd
Several updates

mystocks <- c("her-47d3", "whb-comb", "mac-nea", "hom-west", 
              "ple-nsea", "cod-nsea", "sol-nsea","had-nsea")

demstocks <- c("ple-nsea", "cod-nsea", "sol-nsea","had-nsea")
pelstocks <- c("her-47d3", "whb-comb", "mac-nea", "hom-west")

@@

@@

@@

@@

@@

@@

           ggplot(aes(x=year, y=data, group=assessmentyear)) +
           theme_publication() +
           geom_line(aes(colour=decade)) +
           geom_point(data=filter(d1, stockkeylabelold == pelstocks[[i]]), 
                      aes(x=year, y=data, colour=decade),
                      inherit.aes=FALSE) +
           ggrepel::geom_text_repel(
                      data=filter(d1, stockkeylabelold == pelstocks[[i]]),
                      aes(x=year, y=data, colour=decade, label=yr),
                      inherit.aes=FALSE) +
           scale_colour_manual(values=myColors) +
           expand_limits(y=0) +
           labs(x="",y="", title=demstocks[[i]]) +
           facet_wrap(~variable, scales="free_y")
         )
}

@@

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% c(2000, 2010, 2020, 2022)) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

@@

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% c(2000, 2010, 2020, 2022)) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

@@

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% c(2000, 2010, 2020, 2022)) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

>>>>

mystocks <- c("her-47d3", "whb-comb", "mac-nea", "hom-west", 
              "ple-nsea", "cod-nsea", "sol-nsea","had-nsea", "hke-nrtn")

demstocks <- c("ple-nsea", "cod-nsea", "sol-nsea","had-nsea", "hke-nrtn")
pelstocks <- c("her-47d3", "whb-comb", "mac-nea", "hom-west")

@@

assessmentyears         <- c(2015, 2020, 2022)

@@

# iAdvice %>% distinct(stockkeylabelold, assessmentyear) %>% filter(stockkeylabelold=="hke-nrtn") %>% View()
# iAssess %>% distinct(stockkeylabelold, assessmentyear) %>% filter(stockkeylabelold=="hke-nrtn") %>% View()

# iAssess %>% filter(stockkeylabelold=="hke-nrtn", assessmentyear==2010) %>% View()

@@

```{r, echo=FALSE, fig.asp=1.4, fig.align="center", message=FALSE, warning=FALSE}

iAdvice %>% 
  group_by(stockkeylabelold, tacyear) %>% 
  summarize(
    nF = sum(!is.na(fset)),
    nSSB = sum(!is.na(ssbset))
  ) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", nF:nSSB) %>% 
  # mutate(data = ifelse(data==0, NA, data)) %>% 
  filter(data > 0) %>% 
  ggplot(aes(x=tacyear, y=variable)) +
  theme_publication() +
  geom_point(aes(colour=variable)) +
  facet_wrap(~stockkeylabelold)

@@

```{r, echo=FALSE, fig.asp=1.4, fig.align="center", message=FALSE, warning=FALSE}

@@

p1 + p2 + p3 + p4 + p5 + plot_layout(ncol = 1, guides="collect") &
  theme(legend.position='bottom')

@@

           ggplot(aes(x=year, y=data, group=assessmentyear)) +
           theme_publication() +
           geom_line(aes(colour=decade)) +
           geom_point(data=filter(d1, stockkeylabelold == pelstocks[[i]]), 
                      aes(x=year, y=data, colour=decade),
                      inherit.aes=FALSE) +
           ggrepel::geom_text_repel(
                      data=filter(d1, stockkeylabelold == pelstocks[[i]]),
                      aes(x=year, y=data, colour=decade, label=yr),
                      inherit.aes=FALSE) +
           scale_colour_manual(values=myColors) +
           expand_limits(y=0) +
           labs(x="",y="", title=pelstocks[[i]]) +
           facet_wrap(~variable, scales="free_y")
         )
}

@@

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% assessmentyears) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

# iAssess %>% filter(stockkeylabelold=="hke-nrtn", assessmentyear==2010) %>% View()

@@

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% assessmentyears) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

# d2 %>% filter(stockkeylabelold=="hke-nrtn", source=="assess1990") %>% View()

@@

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% assessmentyears) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)
